Scalable Graph-Based Neural \\ Reconstruction for Connectomics

### 2018-03-13 papers/eccv2018/2_method.tex
papers: some updates based on HP comments
papers: added second error case

\begin{figure}[t]
	\centering
	\includegraphics[width=0.32\linewidth]{./figures/split_error1.png}
	\includegraphics[width=0.32\linewidth]{./figures/split_error2.png}		\includegraphics[width=0.32\linewidth]{./figures/merge_candidate2.png}
	\caption{Three erroneously split segments.}
	\label{fig:merge_candidates}
\end{figure}

@@

\paragraph{Post-processing}

By reformulating the segmentation problem as a graph partitioning one, we can enforce some global constraints on our result based on the underlying biology.
Traditional hierarchical clustering algorithms do not rely on such constraints but consider local decisions independently.
We enforce a global constraint that neurons are tree-structured and should not contain cycles. 
The multicut problems returns a series of ``collapsed'' edges between nodes that belong to the same neuron.
We iterate over these edges in order of the probability of merge generated by our CNN. 
We ``collapse'' the edge only if it does not create a cycle in the graph.

>>>>

\begin{figure}[t]
	\centering
	\includegraphics[width=0.32\linewidth]{./figures/split_error1.png}
	\includegraphics[width=0.32\linewidth]{./figures/split_error2.png}		\includegraphics[width=0.32\linewidth]{./figures/split_error3.png}
	\caption{Three erroneously split segments.}
	\label{fig:merge_candidates}
\end{figure}

@@

\subsubsection{Post-processing}

By reformulating the segmentation problem as a graph partitioning one, we can enforce some global constraints on our result based on the underlying biology.
Traditional hierarchical clustering algorithms do not rely on such constraints but consider local decisions independently.
We enforce a global constraint that neurons are tree-structured and should not contain cycles. 
The multicut problems returns a series of ``collapsed'' edges between nodes that belong to the same neuron.
We iterate over these edges in order of the probability of merge generated by our CNN. 
We ``collapse'' an edge only if it does not create a cycle in the graph.

### 2018-03-13 papers/eccv2018/4_results.tex
papers: added second error case

\begin{figure}[t!]
	\centering
	\includegraphics[width=0.45\linewidth]{./figures/merge_candidate1.png}		\includegraphics[width=0.45\linewidth]{./figures/merge_candidate1.png}
	\caption{Two false negative example of our method due to graph pruning. The distance between the endpoints (circled) of the two segments is too far to be flagged as a merge candidate. \TODO{SECOND EXAMPLE}}
	\label{fig:skeleton-results}
\end{figure}

>>>>

\begin{figure}[t!]
	\centering
	\includegraphics[width=0.45\linewidth]{./figures/merge_candidate1.png}		\includegraphics[width=0.45\linewidth]{./figures/merge_candidate2.png}
	\caption{Two false negative example of our method due to graph pruning. The distance between the endpoints (circled) of the two segments is too far to be flagged as a merge candidate.}
	\label{fig:skeleton-results}
\end{figure}
